Deeply Virtual Compton Scattering measurement off bound protons

### 2018-08-09 eg6-letters/incoherent/incoherent_prl.tex
implementing some of the suggestions

\title{Deeply Virtual Compton Scattering measurement off bound proton}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
   accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   proton have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound proton is 
   smaller by $20\%$ to $40\%$, indicating possible medium modification 
   of its partonic structure. This measurement opens a new avenue for 
   studying structure of the bound nucleon and explore the origin of the EMC 
   effect using the framework of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While lepton-nucleon elastic scattering 
measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the partonic structure of the nucleon and 
the longitudinal momentum distributions of the constituent partons, i.e., 
quarks and gluons \cite{pdg}.  With nuclear targets, deeply inelastic lepton 
scattering measurements have revealed the fact that the distribution of quarks 
in a nucleus is not a simple convolution of their distributions within 
nucleons, an observation known as the ``EMC effect''\cite{EMC_first} (for 
reviews on the topic, see  
\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for this process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contain the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

>>>>

\title{Deeply Virtual Compton Scattering measurement off bound protons}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurement of incoherent deeply 
   virtual Compton scattering (DVCS) off $^4$He. The data were accumulated 
   using a 6 GeV longitudinally polarized electron beam incident on a 
   pressurized $^4$He gaseous target placed in front of the CLAS spectrometer 
   in Hall-B at the Thomas Jefferson National Accelerator Facility. The 
   azimuthal angular ($\phi$) dependence of the BSA is studied in a wide range 
   of virtual photon and scattered proton kinematics. The Q$^2$, $x_B$, and $t$ 
   dependencies of the BSA on the bound proton are compared with the one on the 
   free proton. In the whole kinematical region of our measurements, the BSA on 
   the bound proton is smaller by $20\%$ to $40\%$, indicating possible medium 
   modification of its partonic structure. This measurement opens a new avenue 
   for studying structure of the bound nucleon and explore the origin of the 
   EMC effect using the framework of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While lepton-nucleon elastic scattering 
measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the partonic structure of the nucleon and 
the longitudinal momentum distributions of the constituent partons, i.e., 
quarks and gluons \cite{pdg}.  With nuclear targets, deeply inelastic lepton 
scattering measurements have revealed that the distribution of quarks in a 
nucleus is not a simple convolution of their distributions within nucleons, an 
observation known as the ``EMC effect''\cite{EMC_first} (for reviews on the 
topic, see  \cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations can be revealed through deeply virtual Compton scattering (DVCS), 
i.e., the hard exclusive lepto-production of a real photon, which provides 
access to a three-dimensional imaging of partons within the generalized parton 
distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the scattering is off the entire nucleus, which is 
left intact in the final state \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a 
nucleon, which is ejected from the nucleus.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the leading-twist handbag 
diagram for this process. In the Bjorken regime, i.e, large virtual photon 
four-momentum squared ($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant 
momentum transfer ($t=(p-p^\prime)^2$), the DVCS scattering process can be 
factorized, leaving the non-perturbative structure of the nucleon to be 
parametrized in terms of four chirally-even GPDs: $H$, $E$, $\widetilde{H}$, 
and $\widetilde{E}$, representing the four helicity-spin combinations of the 
quark-nucleon states \cite{Freund_Collins,Ji_Osborne}. Experimentally, we 
measure the squared sum of the Bethe-Heitler (BH) and the DVCS amplitudes. The 
BH process, where the real photon is emitted by the incident or the scattered 
electron rather than the nucleon, dominates the cross section at our 
kinematics. The BSA arises from the interference of these two terms and is 
directly sensitive to the DVCS amplitude that contains the information on the 
GPDs. Using a longitudinally polarized electron beam (L) and an unpolarized 
target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.
